Hysteresis in human computation:\\ how one task affects another

### 2014-12-03 docs/publications/2014.09_SCIENCE/man.tex
edits and improvements to figs

\paragraph{Experimental setup.}
\begin{figure}
	\centering
	\includegraphics[scale=0.7]{figs/images.pdf}
	\caption{
		Examples of images used for various experiments and treatments:
		A) initial tasks for \textit{task1:food}, B) initial tasks for 
		\textit{task1:obj}, C) test tasks for treatments in \textit{exp1}, 
		D) initial tasks for \textit{task2:food}, 
		E) initial tasks for \textit{task2:cult},  
		F) test tasks for \textit{exp2}.  The full set of experimental 
		materials is shown in the supplementary text.
	}

@@

In all treatments, workers were shown images one at a time, and had to
provide 5 labels for each.  From the perspective of the worker, there was no
distinction or interruption between the initial and test tasks.  We used
workers' unique identifiers to ensure that they only participated in a 
one treatment of a single experiment.

\setlength{\tabcolsep}{2pt}
\begin{table}[t]
\centering
\begin{tabular}{ c c c c c }
		\hline \noalign{\smallskip}
		\multicolumn{3}{c}{\textbf{Treatment name}} & \parbox[c]{1.6cm}{\centering \textbf{Frame}} & \parbox[c]{1.3cm}{\centering \textbf{Initial\\ tasks}}	\\

@@

		\multirow{6}{*}{ \parbox[c]{0.7cm}{ \phantom{XXX} exp1}} 
			& \multirow{2}{*}{task1} & food & none & food\\
			& & obj & none & objects\\

@@

		\multirow{4}{*}{exp2} 
			& \multirow{2}{*}{task2}  &  food & none & food\\
			& 	&  cult & none & culture\\
			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
			& \multirow{2}{*}{frame2} & food & food & food\\
			& 	& cult & culture & food\\

@@

	\caption{ \footnotesize{ 
		We use the treatment names shown to refer to specific sections of 
		the experimental data.
	}}
	\label{table:treatments}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/theta.pdf}
	\caption{
		Lower-bound estimates for the  worst-case bias introduced in image
		labeling tasks due to worker exposure effects.  The estimate was 
		based on the performance of a multinomial na\"ive Bayes classifier,
		trained to infer HPU exposures. A) Bias induced through various
		modalities and prime concepts (see Table 1). B) Bias induced in 
		\textit{task1}, as a function of test task position.  Error bars
		show the one-tailed 95\% confidence interval.
	}
	\label{fig:theta}
\end{figure}

>>>>

\paragraph{Experimental setup.}
\begin{figure}
	\centering
	\includegraphics[scale=0.7]{figs/images.pdf}
	\caption{
		Examples of images used for various experiments and treatments:
		A) initial task for \textit{task1:food}, B) initial task for 
		\textit{task1:obj}, C) test task for treatments in \textit{exp1}, 
		D) initial task for \textit{task2:food}, 
		E) initial task for \textit{task2:cult},  
		F) test task for treatments in \textit{exp2}.  
		The full set of experimental materials is shown in the 
		supplementary text.
	}

@@

In all treatments, workers were shown images one at a time, and provided five 
labels for each.  From the perspective of the worker, there was no
distinction or interruption between the initial and test tasks.  We used
workers' unique identifiers to ensure that they only participated in a 
one treatment of a single experiment.

\setlength{\tabcolsep}{2pt}
\begin{table}[t]
\centering
\begin{tabular}{ c c c c c }
		\hline \noalign{\smallskip}
		\multicolumn{3}{c}{\textbf{Treatment name}} & \parbox[c]{1.4cm}{\centering \textbf{Frame}} & \parbox[c]{1.3cm}{\centering \textbf{Initial\\ tasks}}	\\

@@

		\multirow{6}{*}{ \parbox[c]{0.8cm}{ \phantom{XX} exp1}} 
			& \multirow{2}{*}{task1} & food & none & food\\
			& & obj & none & objects\\

@@

		\multirow{4}{*}{\parbox[c]{0.8cm}{exp2}} 
			& \multirow{2}{*}{task2}  &  food & none & food\\
			& 	&  cult & none & culture\\
			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
			& \multirow{2}{*}{frame2} & food & food & food\\
			& 	& cult & culture & food\\

@@

	\caption{ 
		We use the treatment names shown to refer to specific sections of 
		the experimental data.
	}
	\label{table:treatments}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/theta.pdf}
	\caption{
		Bias as measured by a na\"ive Bayes classifier, $\theta_\mathrm{NB}$,
		induced in image-labeling tasks, due to framing and 
		intertask effects. 
		A) Bias in the responses to five test tasks,
		measured between the pairs of treatments indicated on the abscissa.  
		B) Bias between the treatments of \textit{task1}, 
		measured for individual test tasks, and plotted as a function of 
		task position.  Error bars show the 95\% confidence intervals.
	}
	\label{fig:theta}
\end{figure}
